Verifying Demonstrations

### 2019-02-28 paper/intro.tex
shortens intro, fixes protocol.tex non-compile problems

While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper. We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
Alice wants to estimate the number of participants to prove a certain support for her cause against Grace.
Bob, Carol and many others participate in the protest.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

@@

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
However, most of them lack precision (\ie they have large error margins) and 
they can only give an estimate for a particular snapshot in time. In particular, the existing methods cannot reliably 
estimate the cumulative participation count --- at least not without counting 
some persons multiple times --- which in turn increases the error of the 
estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. While one cannot
prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.

>>>>

While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper. We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).

@@

Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
Alice wants to estimate the number of participants to prove a certain support for her cause against Grace in a way that is both demonstrably accurate and does not increase the participants' risk of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

Existing methods for crowd-counting vary significantly in terms of approaches.% (we will review them in detail in \cref{related-work}).
Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.  In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
%In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. While one cannot
prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.

### 2019-02-28 paper/protocol.tex
shortens intro, fixes protocol.tex non-compile problems

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.
The protester should also fetch a time-correlated random value, \(\t_s\), from 
\(\TS\), \(t_s\gets \TSget\).

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the protester, commit the proof-share data to the 
ledger, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
%(This is to make the time interval as early as possible, whoever is the faster 
%will submit it.) \sonja{but both do}
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage on the ledger, \(\TSsubmit[\psh_W]\).

\begin{figure*}
  \centering
  \small
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
    \end{align*}
    \caption{Join and participation.}
  \end{subfigure}
  \hfill
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\wid})],\quad \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\pid})],\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
    \caption{Submission.}
  \end{subfigure}
  \caption{%
    An overview of \CROCUS participation.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
   public ledger for permanent storage \(S\). Note that \pid  always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure*}
%\normalsize

>>>>

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.
The protester should also fetch a time-correlated random value, \(t_s\), from 
\(\TS\), \(t_s\gets \TSget\).

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the protester, commit the proof-share data to the 
ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
%(This is to make the time interval as early as possible, whoever is the faster 
%will submit it.) \sonja{but both do}
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage on the ledger, \(\TSsubmit[\psh_W]\).

\begin{figure*}
  \centering
  \small
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
    \end{align*}
    \caption{Join and participation.}
  \end{subfigure}
  \hfill
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      P\colon & t_e\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\wid})],\quad \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\pid})],\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
    \caption{Submission.}
  \end{subfigure}
  \caption{%
    An overview of \CROCUS participation.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
   public ledger for permanent storage \(S\). Note that \pid  always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure*}
%\normalsize
